Potential of I/O Aware Workflows in Climate and Weather

### 2020-05-25 paper.tex
Bigger size for fig 1.
Inserting ref for the SSD

\fig{width=0.8\columnwidth}{pic/cylc1}{Example of a Cylc workflow with its configuration file \cite{8675433}}

@@

Another improvement can be achieved by using local storage.
Each local SSD of Mistral is a Micron M600 MTFD (256\,GB), which has a nominal sequential read/write performance slightly above 500\,MB/s.
Hence, with 500 nodes, we could achieve 250\,GB/s, which surpasses the Lustre performance observed in \cref{pic/data}.
Even more, our 3\,TB of data would be about 6\,GB per node, which could be cached in memory and overlap with the computation phases.
An additional benefit of using local storage is that the interference with I/O activities of other jobs would be minimised.
Actually, for all reasonable sizes of the experimental data with 500+ nodes, the observed performance of node-local storage would be higher, and thus, improving the workflow execution time.
Since DKRZ has more than 3,000 nodes, using the local SSD would sum up to 1.5\,TB/s.
For model runs with 1\,km resolution, such configurations would be reasonable.
It might also be suitable to couple the model with a parallel analysis process directly using an in-memory file system such as \texttt{tmpfs}.
In this case, the performance per node can be assumed to be 3\,GiB/s, making it a viable option for smaller runs.

>>>>

\fig{width=0.9\columnwidth}{pic/cylc1}{Example of a Cylc workflow with its configuration file \cite{8675433}}

@@

Another improvement can be achieved by using local storage.
Each local SSD of Mistral is a Micron M600 MTFD\footnote{https://www.anandtech.com/show/8528/micron-m600-128gb-256gb-1tb-ssd-review-nda-placeholder} (256\,GB), which has a nominal sequential read/write performance slightly above 500\,MB/s.
Hence, with 500 nodes, we could achieve 250\,GB/s, which surpasses the Lustre performance observed in \cref{pic/data}.
Even more, our 3\,TB of data would be about 6\,GB per node, which could be cached in memory and overlap with the computation phases.
An additional benefit of using local storage is that the interference with I/O activities of other jobs would be minimised.
Actually, for all reasonable sizes of the experimental data with 500+ nodes, the observed performance of node-local storage would be higher, and thus, improving the workflow execution time.
Since DKRZ has more than 3,000 nodes, using the local SSD would sum up to 1.5\,TB/s.
For model runs with 1\,km resolution, such configurations would be reasonable.
It might also be suitable to couple the model with a parallel analysis process directly using an in-memory file system such as \texttt{tmpfs}.
In this case, the performance per node can be assumed to be 3\,GiB/s, making it a viable option for smaller runs.
